---
name: R. Dimas Bagas Herlambang
position: Corporate Consultant
address: Algoritma Data Science School
phone: +62 878-5231-3159
www: bagasbgy.com
email: bagasbgy@gmail.com
twitter: bagasbgy
github: bagasbgy
linkedin: dimasbagash
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::moderncv:
    theme: casual
---

```{r setup, include=FALSE}
# chunk set-up
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

# import libs
library(tidyverse)
library(vitae)
```

# About Me

Experienced Data Scientist with a demonstrated history of working in the higher education industry. Skilled in Policy Analysis, Econometrics, Machine Learning, and Deep Learning. Strong research professional with a Bachelor's degree focused in Economics from Universitas Airlangga. Currently working as a Corporate Consultant at Algoritma Data Science Education Center, and handled various business problems through data sciences; from simple data preprocess to how to handle big data, and from general machine learning problems to more complex deep learning tasks.

# Educations

```{r}
cv_data <- tribble(
  ~what, ~when, ~with, ~where, ~why,
  "Bachelor's Degree in Economics", "2014 - 2018", "Universitas Airlangga", "Jln. Airlangga 4-6, Surabaya, Indonesia", "GPA of 3.74"
)

cv_data %>% 
  detailed_entries(what, when, with, where, why)
```

# Experiences

```{r}
cv_data <- tribble(
  ~what, ~when, ~with, ~where, ~why,
  "Corporate Consultant", "Nov 2018 - Aug 2019", "Algoritma Data Science School", "Menara Kadin Indonesia, Jln. H.R. Rasuna Said, Jakarta Selatan, Indonesia", NA,
  "Teaching Assistant", "Jul 2018 - Nov 2018", "Algoritma Data Science School", "Menara Kadin Indonesia, Jln. H.R. Rasuna Said, Jakarta Selatan, Indonesia", NA,
  "Research Assistant", "Feb 2018 - Jul 2018", "Department of Economics, Universitas Airlangga", "Jln. Airlangga 4-6, Surabaya, Indonesia", NA,
  "Senior Researcher", "Jul 2017 - Dec 2017", "Pusat Data Analisis Keuangan Indonesia, Universitas Airlangga", "Jln. Airlangga 4-6, Surabaya, Indonesia", NA,
  "Manager of Research Division", "Oct 2016 - Jul 2017", "Pusat Data Analisis Keuangan Indonesia, Universitas Airlangga", "Jln. Airlangga 4-6, Surabaya, Indonesia", NA
)

cv_data %>% 
  detailed_entries(what, when, with, where, why)
```

\newpage

# Past Organizations

```{r}
cv_data <- tribble(
  ~what, ~when, ~with, ~where, ~why,
  "Vice President", "Dec 2016 - Dec 2017", "Badan Eksekutif Mahasiswa Fakultas Ekonomi dan Bisnis Universitas Airlangga (Student Executive Board)", NA, NA,
  "Chairman", "Dec 2015 - Dec 2016", "Himpunan Mahasiswa Ekonomi Pembangunan Universitas Airlangga (Student Association)", NA, NA
)

cv_data %>% 
  detailed_entries(what, when, with, where, why)
```

# Honors and Awards

```{r}
cv_data <- tribble(
  ~what, ~when, ~with, ~where, ~why,
  "1st Place Winner for Student Category in 4th EJAVEC", "Oct 2017", "Bank Indonesia & Universitas Airlangga", NA, NA,
  "Awardee of Generasi Baru Indonesia Scholarship", "Mar 2016", "Bank Indonesia", NA, NA
)

cv_data %>% 
  detailed_entries(what, when, with, where, why)
```

# Publications - Papers

```{r}
cv_data <- tribble(
  ~what, ~when, ~with, ~where, ~why,
  "Optimizing Demographic Dividend in Perspective of Return on Education in East Java: To School, to Work, or to Entrepreneur?", "Oct 2018", "EJAVEC Journal", NA, NA
)

cv_data %>% 
  detailed_entries(what, when, with, where, why)
```

# Publications - Softwares (R Packages and Projects)

```{r}
cv_data <- tribble(
  ~what, ~when, ~with, ~where, ~why,
  "rucoin: An R API to KuCoin market", "Jun 2019", "https://github.com/bagasbgy/rucoin", NA, NA,
  "tidymodels-examples: A personal collection of tidymodels implementation for various machine learning routines", "May 2019", "https://github.com/bagasbgy/tidymodels-examples", NA, NA,
  "rockerverse-kickstart: A quick start for RStudio server in a container", "Feb 2019", "https://github.com/bagasbgy/rockerverse-kickstart", NA, NA,
  "shiny-retail: A shiny dashboard for monitoring a retail business activity", "Jan 2019", "https://github.com/bagasbgy/shiny-retail", NA, NA,
  "kerasgenerator: Data generator for Keras interface to R", "Jan 2019", "https://github.com/bagasbgy/kerasgenerator", NA, NA,
  "forecasting-lab: A shiny dashboard for forecast modelling and testing", "Oct 2018", "https://github.com/bagasbgy/forecasting-lab", NA, NA
)

cv_data %>% 
  detailed_entries(what, when, with, where, why)
```

\newpage

# Projects

```{r}
cv_data <- tribble(
  ~what, ~when, ~with, ~where, ~why,
  "Course Producer for PT Akur Pratama (Yogya Group)", "Feb 2019", "Algoritma Data Science School", NA, NA,
  "Course Producer for PT Astra Honda Motor", "Nov 2018", "Algoritma Data Science School", NA, NA,
  "Course Producer for PT Kereta Api Indonesia", "Oct 2018", "Algoritma Data Science School", NA, NA,
  "Course Producer for PT Saka Energi Indonesia", "Sep 2018", "Algoritma Data Science School", NA, NA,
  "Course Producer for Algorithmic Trading using R", "Sep 2018", "Algoritma Data Science School", NA, NA,
  "Instructor in Capacity Building for Bank Indonesia, Jember Representative Office", "Jun 2017", "Bank Indonesia, Jember Representative Office", NA, NA,
  "Instructor in Capacity Building for Bank Indonesia, East Java Representative Office", "May 2017", "Bank Indonesia, East Java Representative Office", NA, NA,
  "Regional Economist for BRI, East Java Representative Office", "Apr 2017", "BRI, East Java Representative Office", NA, NA
)

cv_data %>% 
  detailed_entries(what, when, with, where, why)
```

\newpage

# Certifications

```{r}
cv_data <- tribble(
  ~what, ~when, ~with, ~where, ~why,
  "DSAx: Debt Sustainability Analysis", "Dec 2017", "International Monetary Fund", NA, NA,
  "WDR01x: Digital Dividends: Strengthening the Analog Foundation of the Digital Revolution", "Dec 2017", "World Bank Group", NA, NA,
  "Introduction to R Course", "Nov 2017", "DataCamp", NA, NA
)

cv_data %>% 
  detailed_entries(what, when, with, where, why)
```

# Skills - Programming Languages

* R
* python
* Docker
* Apache Drill
* Apache Spark
* Apache Hadoop
* Apache Hive

# Skills - Data Science Proficiencies

* Time Series and Forecasting
* Econometrics
* Deep Learning
* Machine Learning in General